The problem and promise of scale in multilayer networks

### 2019-12-08 paper/introduction.Rmd
clarify skeleton

<!-- Landscape spatial scale -->
Our understanding of ecological patterns and processes are directly linked to the scale at which they are observed [@levin1992].

>>>>

<!-- ### Landscape spatial scale -->
Our understanding of ecological patterns and processes are directly linked to the scale at which they are observed [@levin1992problem].
